% EDUCATION ########################################################################
\cvsection{Education}
\cvevent{3rd Year Bachelor of Computer Science (BCS)}{University of British Columbia}{\medskip September 2022 -- May 2025}{}
\cvevent{BA Cognitive Systems with Specialization in Psychology}{University of British Columbia}{\medskip September 2013 -- May 2018}{}
% \divider

\cvsection{Awards}
\cvevent{Best Paper Award}{11th International Conference on Augmented Cognition}{\medskip 2017}
\cvevent{Trek Excellence Scholarship for Continuing Students}{University of British Columbia}{\medskip 2014}
\cvevent{Dean's List}{University of British Columbia}{\medskip 2014-2017}
\cvevent{Mary Stewart MacInnes Memorial Scholarship}{University of British Columbia}{\medskip 2017}


% SKILLS/COURSEWORK ##############################################################
\cvsection{Relevant Skills}
% Languages
\cvtag{Python}
\cvtag{MATLAB}
\cvtag{HTML}
\cvtag{CSS}
\cvtag{Java}
\cvtag{JavaScript}
\cvtag{Node.js}
\cvtag{Git/GitHub}
\cvtag{LaTeX}
% Tools
\cvtag{Firebase}
\cvtag{Google Analytics}
\cvtag{Firestore}
\cvtag{Data Analysis}
\cvtag{Data Processing}
\cvtag{Marketing}
\cvtag{Copywriting}
\cvtag{Multi-Dimensional Analysis}
\cvtag{Data Visualization}
\cvtag{Data Cleaning}
\cvtag{Regression Analysis}
\cvtag{Fourier Transform}
\cvtag{Clustering Analysis}


% \divider
\cvsection{Languages}
\cvtag{Spanish (fluent)}
\cvtag{French (B2)}
\cvtag{German (B2)}
\cvtag{Portuguese (B2)}
\cvtag{Italian (B2)}
\cvtag{Mandarin (A1)}
\cvtag{Catalan (A2)}
\cvtag{Icelandic (A1)}




% EXTRACURRICULARS ##################################################################
\cvsection{Other Work}

\cvevent{Teaching Assistant - Departments of Cognitive Systems, Psychology}{University of British Columbia}{2016 - 2018}
\begin{itemize}
  \item Led and marked weekly labs; taught students how to build Arduino-based robots to accomplish sensory, motor and primitive environment-based decision-making.
  \item Created teaching materials, including detailed technical and hardware instructions for constructing and operating Arduinos.
\end{itemize}
\divider\small

\cvevent{Research Advisor}{UBC Biomedical Engineering Student Team - Medical Innovation in Neurotechnology}{2017}
\begin{itemize}
  \item Assisted UBC 'BEST' Engineering Team in understanding and designing innovative medical neurotechnology.
  \item Educated and assisted in setting goals for 'BEST' team.
\end{itemize}
\divider\small

\cvevent{\href{}{Gold Tongue App [GitHub]}}{}{2021 -- present}{}
\begin{itemize}
  \item Created machine-learning based software to perceive different speaker phonemes and give immediate feedback on quality of pronunciation and guided instructions to improve. Completely new technology.
  \item Project was accepted into the Pre-Accelerator at Innovation Ottawa and was offered a pilot test with the Federal Government of Canada for in-house employee training.
\end{itemize}
\divider\small

\cvevent{\href{https://link.springer.com/chapter/10.1007/978-3-319-58628-1_3}{Neural Dynamics of Spontaneous Thought[Research Article]}}{}{2016 - 2017}{}
\begin{itemize}
  \item Performed EEG analyses on meditation practitioners to discern the fast neural dynamics of spontaneous thoughts.
  \item Included independent component analysis, time-series analyses, literature review and publishing.
\end{itemize}
\divider\small



